Simulating Ultra High-Dimensional Multivariate Data Using the bigsimr R Package

### 2020-10-19 020-simulation-algorithm.Rmd
add more on the motivating data and some figs

This section describes the method for simulating a random vector $\bf Y$ with $Y_i$ components for $i=1,2,\ldots,d$. Each $Y_i$ has a specified marginal
distribution function $F_i$ and its inverse. To characterize dependency, every pair $(Y_i, Y_j)$ has either a specified Pearson correlation \@ref(eq:pearson), (rescaled) Spearman correlation \@ref(eq:spearmanRescaled) , or Kendall's $\tau$ (Equation \@ref(eq:tau) ). The method only approximately matches the Pearson correlation in general, whereas the rank-based methods are exact.

>>>>

This section describes the method for simulating a random vector $\bf Y$ with $Y_i$ components for $i=1,2,\ldots,d$. Each $Y_i$ has a specified marginal
distribution function $F_i$ and its inverse. To characterize dependency, every pair $(Y_i, Y_j)$ has either a specified Pearson correlation \@ref(eq:pearson), (rescaled) Spearman correlation \, or Kendall's $\tau$ ). The method only approximately matches the Pearson correlation in general, whereas the rank-based methods are exact.

### 2020-10-19 050-motivating-application-and-examples.Rmd
add more on the motivating data and some figs

# Motivating application and examples

@@

```{r runBRCA, echo=TRUE, results=TRUE, cache = TRUE}
## Set the number of random vectors
n <- 10000
## construct margins
nb_margins <- make_nbinom_alist(sizes, probs)
## run sims
system.time( sim_nbinom <- rvec(n, nb_Rho, nb_margins, type = corType,
                                ensure_PSD = TRUE, cores = cores) )
```

>>>>

# Replicating motivating data and example applications

@@

```{r runBRCA, echo=TRUE, results=TRUE, cache = TRUE}
## Set the number of random vectors
n <- 10000
## construct margins
nb_margins <- make_nbinom_alist(sizes, probs)
## run sims
system.time( sim_nbinom <- rvec(n, nb_Rho, nb_margins, type = corType,
                                ensure_PSD = TRUE, cores = cores) )
colnames(sim_nbinom) <- names(brca)
```

Figure X.

```{r simDataFig, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap='Simulated data for 3 randomly selected high-expressing genes, replicating the real data structure describing in the Introduction.'}
## retrieve the examples from an earlier chapter
## there is probably a better way to do this
exampleGenes <- readRDS(file = './data/exampleGenes.rds') 
GGally::ggpairs(data = as.data.frame(sim_nbinom[ ,exampleGenes] ))
```

### 2020-10-19 index.Rmd
add more on the motivating data and some figs

```{r serveHelper, include=FALSE, eval=FALSE}
## rmote::start_rmote()
## library(ggplot2); qplot(mpg, wt, data=mtcars, colour=cyl)
## bookdown::render_book("index.Rmd", "bookdown::pdf_book")
bookdown::serve_book()
```

@@

>>>>

```{r serveHelper, include=FALSE, eval=FALSE}
## rmote::start_rmote()
## library(ggplot2); qplot(mpg, wt, data=mtcars, colour=cyl)
## bookdown::render_book("index.Rmd", "bookdown::pdf_book")
## bookdown::preview_chapter("index.Rmd")
bookdown::serve_book()
```

@@

## Motivating example

- RNA-seq
- Provide a table of values
- check the talk history

```{r realDataTabl, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE}
## Describe and plot real data
brca <- readRDS(file = './data/brca99.rds')
set.seed(10192020)
exampleGenes <- colnames(brca)[sort(sample(ncol(brca), 3))]
saveRDS(exampleGenes, file = './data/exampleGenes.rds')
kable(round(brca[1:4, exampleGenes]))
## GGally::ggpairs(data = as.data.frame(brca[ ,exampleGenes] ))
```

Figure X.

```{r realDataFig, echo = FALSE, eval=TRUE, message=FALSE, warning=FALSE, fig.width= 8, fig.align='center', fig.cap='Real data for the 3 selected high-expressing genes'}
## Describe and plot real data
GGally::ggpairs(data = as.data.frame(brca[ ,exampleGenes] ))
```
